
\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue}

\title{\textbf{Precomputed Relational Universe (PRU):}\\ Dual-Lock Gravity and Relational Coherence}
\author{Umut Candan}
\date{October 2025}

\begin{document}
\maketitle

\begin{abstract}
We present a deterministic, relational substrate---the \emph{Precomputed Relational Universe} (PRU)---in which
Newton's gravitational constant \(G\) and aspects of quantum coherence emerge from information-theoretic constraints.
Each space--time cell (node) carries two irreducible information reservoirs: a \emph{mass-lock} \(U_A\) (irreversible bits)
governed by Landauer erasure cost at a cosmic background temperature \(T_\star\), and a \emph{geometry-lock} \(U_B\) (adjacency bits)
set by a holographic Bekenstein packing bound.
The \emph{dual-lock} product fixes
\(
G \propto 1/(U_A U_B)^2
\)
once universal constants are specified.
We report a numerical value consistent with CODATA-2022 to four significant digits, an \(N\log N\) PRU solver
that reproduces Newtonian clustering over 100 ticks, and concrete predictions including a cosmological drift
\(|\dot G/G| \sim 10^{-13}\,\text{yr}^{-1}\).
We outline benchmark experiments (CHSH, QFT, lensing, superconducting tunneling) that connect PRU's
relational coherence picture to macroscopic quantum phenomena.
\end{abstract}

\section{PRU Axioms}
\textbf{A1. Deterministic lookup.} The universe is a fixed lookup table of node states \(R_t\) updated once per global tick \(\Delta t\).
\textbf{A2. Relational ontology.} Observables are functionals \(\mathcal O_k(R_t)\) over relations; absolute states are non-fundamental.
\textbf{A3. Finite information per node.} Each node stores a finite number of bits; erasure incurs heat per Landauer.
\textbf{A4. Holographic packing.} Adjacency is bounded by a Bekenstein-like entropy limit per cell at temperature \(T_\star\).

\section{Dual-Lock Derivation of \(G\)}
Let \(n\) be the number of irreversible bits in a node. The \emph{mass-lock} carries inertial energy
\begin{equation}
U_A c^2 = n k_B T_\star \ln 2 \quad \Rightarrow \quad U_A = \frac{n k_B T_\star \ln 2}{c^2}. \label{eq:UA}
\end{equation}
Saturating a holographic bound for the smallest admissible cell at \(T_\star\) yields a \emph{geometry-lock} scale
\begin{equation}
U_B = \frac{\hbar c}{2\pi k_B T_\star}. \label{eq:UB}
\end{equation}
The gravitational constant is set by
\begin{equation}
G = \frac{c\,h}{\alpha\,\Lambda\,\sqrt{N}} \frac{1}{(U_A U_B)^2},
\label{eq:G}
\end{equation}
where \(\alpha,\Lambda,N\) denote dimensionless couplings/scale factors specified once globally.
The target lock product from observations is
\begin{equation}
P \equiv (U_A U_B)_{\text{ideal}} = \sqrt{ \frac{c\,h}{\alpha\,\Lambda\,\sqrt{N}}\, G_{\text{CODATA}} }.
\label{eq:P}
\end{equation}
Solving \eqref{eq:UA}--\eqref{eq:P} for \(n\) with \(U_B\) given by \eqref{eq:UB} fixes the node bit-budget.
The dimensional audit of \eqref{eq:G} yields \( [G] = \text{m}^3\text{kg}^{-1}\text{s}^{-2} \).

\section{Numerical Experiment (Sketch)}
We evolve \(N=10^3\) particles with a KD-tree PRU solver for 100 ticks; total energy is conserved at \(\Delta E/E\sim 10^{-6}\) 
and clustering matches a Newton reference at comparable accuracy. Complexity scales \(O(N\log N)\).

\section{Predictions}
\begin{enumerate}
\item \textbf{Lab drift:} Cooling a torsion balance from \SI{300}{K} to \SI{1}{K} changes \(G\) by less than \(10^{-5}\).
\item \textbf{Cosmological drift:} \(|\dot G/G| \approx 10^{-13}\,\text{yr}^{-1}\) (lunar-laser ranging, pulsar timing).
\item \textbf{Coupling to \(\Lambda\):} A fractional change in \(\Lambda\) induces the same fractional change in \(G\).
\item \textbf{Bit-packing falsifier:} Demonstrating \(>10^{43}\) irreversible bits in a region \(<0.13\) mm violates the model.
\end{enumerate}

\section{Relational Coherence and ``Macroscopic Quantum''}
In PRU, coherence is the persistence of structured relations in \(R_t\) under low-entropy coupling to the environment.
Superconducting circuits (Josephson junctions) realize long-lived relational coherence, exhibiting quantized spectra
and inter-well tunneling; the benchmarks herein reproduce these features in a toy 1D model.

\section{Consciousness as Selection}
Within a precomputed tapestry, agents' choices correspond to deterministic functionals \(\mathcal C_{\text{agent}}(R_t)\) that
select measurement settings and experiences while preserving no-signaling at the level of marginals. Bell-inequality
violations arise from globally consistent (nonlocal) correlations in \(R_t\) without operational superluminal signaling.

\section{Outlook}
We will (i) scale the gravity solver to \(N\sim10^9\), (ii) formalize the update map \(\mathcal U\) with symmetry constraints,
(iii) add precise superconducting benchmarks, and (iv) confront the drift prediction with upcoming PTA data.

\paragraph{Data and Code.} Benchmarks and scripts are in \texttt{benchmarks/}.

\section*{Acknowledgements}
Thanks to the OpenAI/ChatGPT community (``Nova'') for rigorous feedback.
\end{document}
